---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scrapol

<!-- badges: start -->
<!-- badges: end -->

The goal of `scrapol` is to facilitate academic study on American city council representatives whose information is publicly available on [Ballotpedia](https://ballotpedia.org/). This package enables users to gather politicians' party and district information based solely on a url. Users could either utilize `ScrapingParty()` and `ScrapingDistrict()` to collect party and district information respectively or leverage the `scrapol_city()` function to gather both information simultaneously.

This package was tailored for American city council members, although the `ScrapingParty()` function can be used to scrape party information generally. 

The package might be updated in the future with two aims.

1. To accommodate the need of data collection for state- and federal-level politicians.
2. Based on a test of 1,041 city council members, the present version of the package can achieve an accuracy rate of 91.65%  (954/1041\*100%) and 95.49% (994/1041\*100%) in terms of parsing party and district information. I will likely modify the code to further improve the accuracy rate.

# pqview
Visualizing probabilities and quantiles in four widely used continuous distributions

```{r}
1+1
```
